Comparative Analysis of the wav2vec 2.0 Feature Extractor

### 2023-03-03 main.tex
add text, mainly experiments

\section{Methods}
We always normalize the waveform to zero mean and unit variance.
Then, it is input to a \fe.
The \fe is followed by the remaining \gls{AM}.
While the separation between \fe and remaining \gls{AM} is not sharp for neural feature extraction, we always refer to the part that replaces the traditional feature extraction as \fe.

@@

\subsubsection{Supervised Convolutional Features}
As an alternative comparable neural feature extraction method, we use \gls{SCF} \cite{tuske2018:waveform}.
Similarly, a convolutional filterbank with learnable parameters is applied to the waveform.
As in the case of Gammatones, a temporal integration is performed over each channel.
However, in this case multiple filters are used for temporal integration allowing for multi-resolutional processing.
Additionally, these filters are learned during training.
We set the size of the first filterbank to 256, its strides to 10 and the number of channels to 150.
The second convolutional filter applies 5 temporal integration filters with a size of 40 and strides of 16 each.
Since the output of all 5 filters is stacked, we have a resulting feature dimension of 750.
The total receptive field of the \gls{SCF} is \ms{9999}.

\section{Experiments}
\subsection{Model Sizes}
By default, I use 40k parameters for i6 features compared to 4M for \wvtwo.
Can we improve the performance by making the model larger?
\subsubsection{wav2vec 2.0 Components}
To understand where \wvtwo uses the parameters and how much they contribute to the \gls{FE}'s performance, we run it with different configurations.
The results for different widths and depths are shown in \refTab{table:features_w2v_size}.
% Kernel sizes and strides were chosen as (10, 3, 3, 3, 3, 2), (5, 2, 2, 2, 2, 2) for 6 layers, (10, 6, 3, 3, 3), (5, 4, 2, 2, 2) for 5 layers, (10, 6, 6, 3), (5, 4, 4, 2) for 4 layers, (20, 6, 6), (10, 4, 4) for 3 layers, (32, 20), (16, 10) for 2 layers and (320), (160) for 1 layer.
While a larger inner dimension leads to a better performance, no major effect can be observed regarding the number of layers.
The final projection additionally improves the performance, see \refTab{table:features_w2v_proj}.
We can additionally vary the kernel size and final norm.

@@

{
\color{red}
\section{To Dos/Questions}
\begin{itemize}
  \item \wvtwo feature extractor vs. feature encoder
\end{itemize}
}

>>>>

\section{Methods}
This work compares different \fes' applicability for \gls{ASR}.
We always normalize the waveform to zero mean and unit variance before it is input to a \fe.
The \fe is followed by the remaining \gls{AM}.
While the separation between \fe and remaining \gls{AM} is not sharp for neural feature extraction, we always refer to the part that replaces the traditional feature extraction as \fe.

@@

\subsubsection{Supervised Convolutional Features}
As an alternative comparable neural feature extraction method, we use \gls{SCF} \cite{tuske2018:waveform}.
Similarly, a convolutional filterbank with learnable parameters is applied to the waveform.
As in the case of Gammatones, a temporal integration is performed over each channel.
However, in this case multiple filters are used for temporal integration allowing for multi-resolutional processing.
Additionally, these filters are learned during training.
By default, we set the size of the first filterbank to 256, its strides to 10 and the number of channels to 150.
The second convolutional filter applies 5 temporal integration filters with a size of 40 and strides of 16 each.
Since the output of all 5 filters is stacked, we have a resulting feature dimension of 750.
The total receptive field of the \gls{SCF} is \ms{9999}.

\subsection{Acoustic Model}
The \gls{AM} mainly consists of \gls{VGG} \addref blocks for downsampling and 12 \conformer blocks.
The \gls{VGG} downsampling uses three 3x3-convolutional layers with 32, 64 and 64 channels, respectively.
In total, a subsampling factor of 4 in the time dimension is achieved by the strided convolutions so that the \conformer operates on frames with a shift of \SI{40}{\milli\second}.
The feature dimension is reduced by a factor of 2 due to max pooling and then multiplied by the number of channels in the last convolution resulting in a total increase by factor 32 in our case.
\draft{
There is a linear layer and dropout here.
The \conformer blocks should be described here.
}
The configuration follows the setup in \cite{zeineldeen2022robustconformer} \TODO{check!}.

\subsection{Connectionist Temporal Classification}
We use a \gls{CTC} model for our experiments.
It follows the setup described for the \gls{CTC} model in \cite{zhou2022efficient}.
\TODO{Cite Wei's paper and add more description of the CTC model.}
All models are trained in a purely supervised fashion unless explicitly stated otherwise.
\TODO{Do we use an LM?}

\section{Experimental Setup}
\subsection{Data}
We conduct experiments on the 960h LibriSpeech corpus \cite{panayotov2015librispeech}.
For the experiments using a pre-trained \wvtwo \fe, the same 960h were used in pre-training.
\draft{The \gls{LM} was trained on the default LibriSpeech \gls{LM} training data which includes the transcriptions of the training set along with the additional
800M-word text-only data.}
The evaluation is done on the standard \devclean, \devother, \testclean and \testother sets.

\subsection{Training Details}
\draft{We follow the setup in \TODO{Wei's paper} \addref.}
The batch size is 640k samples, which corresponds to \SI{40}{\second} of speech waveform and the gradients are accumulated over 3 steps.
The \TODO{NAdam} optimizer uses a \gls{OCLR} schedule with a peak learning rate of \TODO{X} as described in .
Each model is trained on a single \gls{GPU}.
\TODO{What about chunking? More details needed?}

\section{Results}
\subsection{Model Sizes}
By default, I use 40k parameters for i6 features compared to 4M for \wvtwo.
Can we improve the performance by making the model larger?
\subsubsection{wav2vec 2.0 Components}
To understand where \wvtwo uses the parameters and how much they contribute to the \gls{FE}'s performance, we run it with different configurations.
The results for different widths and depths are shown in \refTab{table:features_w2v_size}.
% Kernel sizes and strides were chosen as (10, 3, 3, 3, 3, 2), (5, 2, 2, 2, 2, 2) for 6 layers, (10, 6, 3, 3, 3), (5, 4, 2, 2, 2) for 5 layers, (10, 6, 6, 3), (5, 4, 4, 2) for 4 layers, (20, 6, 6), (10, 4, 4) for 3 layers, (32, 20), (16, 10) for 2 layers and (320), (160) for 1 layer.
While a larger inner dimension leads to a better performance, no major effect can be observed regarding the number of layers.
The final projection additionally improves the performance, see \refTab{table:features_w2v_proj}.
We can additionally vary the kernel size and final norm.

@@

{
\color{red}
\section{To Dos/Questions}
\begin{itemize}
  \item \wvtwo feature extractor vs. feature encoder
  \item check for arxiv citations
\end{itemize}
}
